\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{titlesec}

\titleformat{\section}[block]{\Large\bfseries}{}{0em}{}
\titleformat{\subsection}[block]{\large\bfseries}{}{0em}{}

\title{Howzatt! Cricket Scorekeeper\\\large Project Report}
\author{Mahak\\Roll No: 24b1017}
\date{\today}

\begin{document}

\maketitle
\begin{abstract}
This project report presents "Howzatt! Cricket Scorekeeper", a web application developed using HTML, CSS, and JavaScript. It allows users to set up teams, update live match scores, view detailed scorecards, and access match summaries. The application simulates real-time cricket scoring and is designed to be intuitive and responsive.
\end{abstract}

\tableofcontents
\newpage

\section{Introduction}
Cricket is a game enjoyed by millions. This project aims to create a lightweight, interactive web-based scorekeeping app for cricket matches. It was developed as a frontend project using core web technologies.

\section{Objectives}
\begin{itemize}
    \item Create a web interface for managing cricket scores.
    \item Track live match updates: runs, wickets, overs.
    \item Maintain a scoreboard and match summary.
    \item Provide a user-friendly UI.
\end{itemize}

\section{Technologies Used}
\begin{itemize}
    \item HTML5 - for page structure.
    \item CSS3 - for styling and layout.
    \item JavaScript - for dynamic updates and logic.
\end{itemize}

\section{System Architecture}
The app consists of multiple HTML pages (setup, live, scorecard, summary), styled with CSS and powered by JavaScript logic in \texttt{score.js}. User inputs from the setup page are stored in \texttt{sessionStorage}, and subsequent pages fetch and display updated data in real time.

\section{Screenshots and Page Descriptions}
% Replace with real screenshots later
\begin{itemize}
    \item \textbf{setup.html:} Used to input team names and match configuration.
    \item \textbf{live.html:} Live match interface to update scores and track overs.
    \item \textbf{scorecard.html:} Displays detailed stats per player.
    \item \textbf{summary.html:} Shows final match summary including winner and total scores.
\end{itemize}

\section{Code Structure and Explanation}
The core logic is in \texttt{score.js}. It handles:
\begin{itemize}
    \item Ball-by-ball updates
    \item Tracking wickets, overs, and strike rotation
    \item Managing session data for state persistence
    \item DOM updates for displaying scores
\end{itemize}

\subsection{Sample JavaScript Snippet}
\begin{lstlisting}[language=JavaScript, basicstyle=\ttfamily\small, breaklines=true]
function addRun(runType) {
    let runs = runType === 'wd' || runType === 'nb' ? 1 : parseInt(runType);
    battingScore.runs += runs;
    if (runType === 'wd' || runType === 'nb') {
        battingScore.extras += 1;
    } else {
        battingScore.balls += 1;
        battingScore.overs = updateOvers(battingScore.overs);
    }
    updateDisplay();
}
\end{lstlisting}

\section{Challenges Faced}
\begin{itemize}
    \item Managing strike rotation logic
    \item Handling page reloads with sessionStorage
    \item Creating responsive layout for different screen sizes
\end{itemize}

\section{Future Improvements}
\begin{itemize}
    \item Add localStorage/database for persistent data.
    \item Include player stats and graphs.
    \item Build a mobile app version.
\end{itemize}

\section{Conclusion}
"Howzatt! Cricket Scorekeeper" is a successful implementation of a single-page web app for cricket scoring. It meets all basic functionality and lays the groundwork for future enhancements.

\section*{References}
\begin{itemize}
    \item MDN Web Docs - HTML/CSS/JavaScript
    \item W3Schools
\end{itemize}


\end{document}
